\section{Project Schedule and Expected Milestones}
\label{plan-section}

The PI has broken the proposed activities into subtasks with
tentative milestones:


1. Ongoing Empirical Studies to mine a large-scale parrallel corpus of
text and code.
   
2. Work on Context-aware Inferrence of Relevant APIs to a Textual Query.

3. Work on Deriving Fully-Qualified Types for APIs in Incomplete Code
in StackOverflow.


4. API Usage Code Synthesis: Models, Representations, and
Methodologies

\hspace{0.1in}   3.1. Graph-based Representations

\hspace{0.1in}   3.2. Graph Synthesis Models and API usage code synthesis.


4. Integrating Code Synthesis into Developer Assistance Tools

\hspace{0.1in}   4.1. Developer assistance tools in IDE.

\hspace{0.1in}   4.2. Web-based developer assistance tools.


5. The integration of the associated tools and their
deployment/training for evaluation, and

6. Evaluation, education, dissemination, and publications.

%====================================================================

\noindent {\bf Year 1}: We focus our ongoing effort to expand our
ongoing on empirical studies in task 1. We will focus also on tasks 2
and 3, and expect to finish task 2 by the end of year 1.

\noindent {\bf Year 2}: We will finish task 2 in the first 3 months of
this year. Tasks 3,4, and 5 will be in our focus in year~2.

\noindent {\bf Year 3}: The prototype integration will
begin. Publications will begin as soon as we have new results.
Education dissemination will start. We will focus on evaluation, and
continue publications and dissemination.

%The foundation consists of both the open architectural CM (task 1) and
%the formulation of flow control and configurable policies (task 2). By
%the end of year 1, we expect to finish task 2. Task 1 could last
%around 14-15 months.

%Year 2: We will start the implementation of that CM architecture
%and supporting tools. In this year, more study will be done for
%conflict problem in GSD

%We also begin the implementation of associated tools for CCM in task
%4. Model merge/synchronization framework (task 5) will be
%continued. Education components will be implemented and publications
%will begin to pick up.

%Year 3: We will change our focus to CCM model and the implementation
%of its associated tools (tasks 4 and 5). Some testing and integration
%will begin. We will continue the publication and dissemination.

%Year 4: We expect to produce most of important results in tasks
%1,2,3,4, and 5. The evaluation will begin.

%Year 5: We will focus on evaluation, testing, integration, and
%continue the publications and dissemination.
