\section{PI's Prior Relevant NSF Supports and Qualifications for this Project}
\label{prior-section}

CCF-1723215, \$260,709, 07/01/16-30/06/18, ``Collaborative
Research: Exploiting the Naturalness of Software''. 
%
\noindent {\bf Intellectural Merit.} The work has three thrusts of
research: (1) Investigating the integration of semantic information
including data types, semantic roles, etc., into a language model, (2)
Developing an accurate code-completion tool using statistical semantic
language model, and (3) Developing a statistical machine translation
model for language migration.
%
\noindent {\bf Broader Impact.} We will transform practical software
engineering tools, using statistical NL techniques, introducing new
generations of (a) code suggestion, completion, and correction tools,
(b) assistive tools for programmers, (c)
summarization, (d) retrieval, and (e) porting tools.  Our work will
help reduce the dominant maintenance component of the software
industry.

%making software development more accessible, enjoyable and productive;
%and therefore will broadly enhance the value that software
%professionals deliver to business and society.

%Dr. Nguyen is currently the PI of the NSF-funded project, ``
%Collaborative Research: Exploiting the Naturalness of Software'', that
%will end August 2018. The work has three thrusts of research.  (1)
%Investigating the integration of semantic information including data
%types, semantic roles, etc., into a language model, (2) Developing an
%accurate code-completion tool using statistical semantic language
%model, and (3) Developing a statistical machine translation model for
%language migration. So far, the majority of the tasks have been
%%completed except empirical evaluation in a real-word setting is
%needed. 

The project has been resulting several publications at top-tier SE
conferences including ICSE
papers~\cite{icse05,icse07,icse09,icse10,icse11}, FSE
papers~\cite{fse06,fse09,fse11}, ASE
papers~\cite{ase06,ase08,ase08-2,ase09,ase10,ase11-phpsync,ase11-bugscout,ase11-idiff},
OOPSLA papers~\cite{oopsla04,oopsla06,oopsla10}, and TSE
papers~\cite{tse08,tse11}.

%Several papers on our results were published through ICSE
%2010~\cite{icse10}, ASE 2010~\cite{ase10}, OOPSLA
%2010~\cite{oopsla10}, ICSM 2010~\cite{icsm10}, ICSE
%2011~\cite{icse11,nier11-1,nier11-2}, FSE 2011~\cite{fse11}, ASE
%2011~\cite{ase11-phpsync,ase11-bugscout,ase11-idiff}, and an IEEE TSE
%journal article~\cite{tse11}.

%Our next phase will be involved more with the tasks (2) and (3).

%Dr. Nguyen is currently an PI on a NSF-funded project: \#CCF-1018600,
%``Find and Fix Similar Software Bugs'', 08/15/2010 through
%07/31/2013. In this project, an empirical study will be conducted to
%collect, analyze, and understand the nature and characteristics of
%recurring and similar bugs within one and across multiple
%systems. This project is expected to advance software engineering
%knowledge on the theoretical foundation, concepts, practical
%techniques, and automated tools to (1) capture the characteristics and
%measure the similarity of code units involved in prior known fixed
%bugs, (2) identify the locations of potential buggy units and derive
%the guidelines to fix them by matching them to the relevant peer code
%units of the known bugs, and (3) support the similar bug detection and
%fixing process. Teaching modules and validation efforts in this
%project will involve students and professionals, promoting teaching
%and training software quality assurance.

%Dr. Nguyen is an expert in software building, software configuration
%management (SCM), and software refactoring. His research work on SCM
%has been published at various prestigious software engineering
%journals and conferences including clone-aware configuration
%management and operation-based version control (TSE'11~\cite{tse11},
%FASE'10~\cite{fase10}, ASE'09~\cite{ase09}), software
%refactoring-aware SCM and software merging (TSE'08 \cite{tse08},
%ICSE'07~\cite{icse07}, FSE'06~\cite{fse06}, OOPSLA'06
%demo~\cite{oopsla06}), object-oriented configuration management
%(ICSE'07~\cite{icse07}, WWW'06~\cite{www06}, ICSE'05~\cite{icse05},
%ICSM'05~\cite{icsm05}).

His other software maintenance works include clone-related bug
detection (TSE'11 \cite{tse11}), bug localization
(ASE'11~\cite{ase11-phpsync}), bug localization from bug reports
(ASE'11~\cite{ase11-bugscout}), recurring bug detection
(ICSE'10~\cite{icse10}), API misuse detection
(OOPSLA'10~\cite{oopsla10}, FSE'09~\cite{fse09}), recurring
vulnerabilities detection (ASE'10~\cite{ase10}), etc.  He was a
Program Co-Chair of the 32nd ACM/IEEE International Conference on
Automated Software Engineering (ASE 2017).

Since 2009, he has been awarded {\bf 4 ACM SIGSOFT Distinguished Paper
Awards, one Best Paper Award, and one best ICSE Formal Research
Demonstration Award} at the top-tier, international software
engineering conferences including ICSE, FSE, and ASE. He is the
Co-Chair of the Formal Research Demo Track at the 40th International
Conference on Software Engineering (ICSE 2018) and the International
Symposium on the Foundations of Software Engineering (FSE 2018). He
has served on Program Committees and Program Boards of top-tier
software engineering conferences: ICSE, FSE, ASE, OOPSLA,
ECOOP.


%Since 2005, his work has been resulting several publications at
%top-tier SE conferences including 5 ICSE
%papers~\cite{icse05,icse07,icse09,icse10,icse11}, 3 FSE
%papers~\cite{fse06,fse09,fse11}, 8 ASE
%papers~\cite{ase06,ase08,ase08-2,ase09,ase10,ase11-phpsync,ase11-bugscout,ase11-idiff},
%2 WWW papers~\cite{www04,www06}, 3 OOPSLA
%papers~\cite{oopsla04,oopsla06,oopsla10}, and 2 FASE
%papers~\cite{fase09,fase10}, 2 TSE papers~\cite{tse08,tse11}.
